---
title: "R Workshop Day 2: R Notebooks and Markdown"
author: "Mike Burnham"
date: "`r format(Sys.time(), '%d %B, %Y')`" # How would we change the format of the date?
output: html_notebook 
#output: pdf_document
# Add things like index Code folding to the preamble
---
R notebooks are handy for producing HTML and PDF documents. I recommend using them for your homework assignments in the methods courses. R notebooks are wrtten in R markdown and chunks of R code. R Markdown is a version of Markdown, a commonly used markup language used for creating formatted documents.

# Section headers
## Level 2 headers
### Level 3 headers
#### Level 4 headers
##### Level 5 headers
###### Level 6 headers

**Bold text**

*Italics*

$Math Mode$

$y = 5x + 3$

## Hot Keys
A few simple hotkeys will go a long way in helping you keep your hands on the keyboard and working faster.

- **Run a line of code**: *Ctrl + Enter*
- **Run a block of code**: *Ctrl+Shift+Enter*
- **Save script/notebook**: **Ctrl+S**
- **Move cursor to the beginning of the line**: *Home*
- **Move cursor to the end of the line**: *End*
- **preview document**: *Ctrl+Shift+K*
- **Create a new code chunk**: *Ctrl+Alt+I*

```{r}
print('hello world')
plot(cars)
```


```{r fig.height=5, fig.width=5, message=TRUE, warning=TRUE, paged.print=FALSE}
plot(cars)
```


```{r, echo=FALSE, results='hide', fig.keep='all'}
print("I'm hidden!")

sum(cars$speed)
```

